Toward theories of deliberated preferences

### 2020-11-12 simple.tex
Better explan incompl

Not mandating Theory completeness is a first important element to allow hope that effective theories of \ac{DJ} can be built.

That the \ac{DJ} of an individual exists independently of any theory of decision making might be considered a strong assumption, by analogy to the case of shallow preferences: psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation. Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.

With no intent of reducing the importance of these findings, it is important to qualify such statements. In supplement to them being not necessarily applicable to reflective preferences, the findings of psychologists do not, evidently, show that all preference statements are labile. As \citet[p.\ xvi]{lichtenstein_construction_2006} write, “To be sure, there are limits to the process of construction. Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings. It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that ‘there is no there there’.”
\commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture. Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}

This remark points towards the importance of allowing for incomplete theories of reflective preferences. \commentYM{définir ce qu'il faut entendre ici par "incomplete"} 
As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
From this does not follow that \acp{DJ} do not exist, but that someone’s \ac{DJ} should not be considered to be necessarily complete. 
\TODO{Check Mandler.}
The definitions of the theories presented here accordingly tolerate both theory incompleteness, which permits the theory to stay silent on some of the propositions in the agenda, and, more fundamentally, deliberation incompleteness, which permits to tolerate that for some propositions, neither it nor its negation figure in someone’s \ac{DJ}.

>>>>

Not mandating Theory completeness is a first important element to allow hope that effective theories of \ac{DJ} can be built. 
To understand why, an analogy with the case of shallow preferences may be useful.
Psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation. Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.
But, with no intent of reducing the importance of these findings, it is important to qualify such statements. 
The findings of psychologists do not, evidently, show that all preference statements are labile. As \citet[p.\ xvi]{lichtenstein_construction_2006} write, “To be sure, there are limits to the process of construction. Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings. It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that ‘there is no there there’.”
\commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture. Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}
This observation justifies propositions that obtain only partial shallow preference models: a shallow statement preference would be considered to exist only when it stays intact under all framings considered relevant. The proposal of \citet{bernheim_beyond_2009} may be understood under that light.

This remark points towards the importance of allowing for incomplete theories of reflective preferences. \commentYM{définir ce qu'il faut entendre ici par "incomplete"} 
As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
From this does not follow that \acp{DJ} do not exist, but that someone’s \ac{DJ} should not be considered to be necessarily complete. 
\TODO{Check Mandler.}
This observation also offers a way of reconciling the remark of \citet{roy_comparison_1995} cited in \cref{sec:informal} and the objectivity of the conclusions of a decision theoretic approach: if, for some propositions, both the proposition and its contrary proposition can be held, with no argument being strong enough to impose one of them, let neither these propositions nor their contrary be part of $i$’s \ac{DJ}; and let the theorist focus on the subset of propositions for which argumentative stability can be found.

The definitions of the theories presented here accordingly tolerate both theory incompleteness, which permits the theory to stay silent on some of the propositions in the agenda, and, more fundamentally, deliberation incompleteness, which permits to tolerate that for some propositions, neither it nor its negation figure in someone’s \ac{DJ}.
